Bayesian Deep Gaussian Processes for Correlated Functional Data: \\ A Case Study in Cosmological Matter Power Spectra

### 2025-06-30 paper/main.tex
minor tweaks/updates to paper

For each cosmology, Mira-Titan contains a batch of 18 simulated power spectra: an inexpensive 
power spectrum estimated from perturbation theory ($y_p$), 16 power spectra estimated from 
low resolution simulations ($y_{\ell_r}, r \in \{1,\dots,16\}$), and one power spectrum from 
a high resolution simulation ($y_h$). 
These power spectra are represented as a function of wavenumber $k$.  Following 
\cite{moran2023mira}, we model on the emulation space 
$\mathcal{P}(k)=\log_{10}\left(\frac{k^{1.5}P(k)}{2\pi^2}\right)$, where $P(k)$ represents the
original spectra. Output is available for $n=351$ values of $k$, spanning
$0.001 \leq k \leq 5$, but each data type has unique wavenumber ranges
where it is deemed approximately unbiased. For $k<0.04$, only $y_p$ provides a reliable 
estimate of the true spectra. $y_{\ell_r}$ are valid for $0.04 \leq k \leq 0.25$, and 
$y_h$ is valid for $0.04 \leq k \leq 5$.  Figure \ref{fig:plot_data} shows an example 
of the output for a particular cosmology. When we focus on $k$ values where $y_{\ell_r}$ 
is valid (center panel), the spatially correlated fluctuations of the low-resolution and 
high-resolution runs becomes apparent.

>>>>

For each cosmology, Mira-Titan contains a batch of 18 simulated power spectra: an inexpensive 
power spectrum estimated from perturbation theory ($y_p$), 16 power spectra estimated from 
low resolution simulations ($y_{\ell_r}, r \in \{1,\dots,16\}$), and one power spectrum from 
a high resolution simulation ($y_h$). 
These power spectra are represented as a function of wavenumber $k$, expressed in units of 
$\text{Mpc}^{-1}$ (inverse megaparsecs).  Following 
\cite{moran2023mira}, we model on the emulation space 
$\mathcal{P}(k)=\log_{10}\left(\frac{k^{1.5}P(k)}{2\pi^2}\right)$, where $P(k)$ represents the
original spectra. Output is available for $n=351$ values of $k$, spanning
$0.001 \leq k \leq 5 \text{ Mpc}^{-1}$, but each data type has unique wavenumber ranges
where it is deemed approximately unbiased. For $k<0.04 \text{ Mpc}^{-1}$, only $y_p$ provides a reliable 
estimate of the true spectra. $y_{\ell_r}$ are valid for $0.04 \leq k \leq 0.25 \text{ Mpc}^{-1}$, and 
$y_h$ is valid for $0.04 \leq k \leq 5 \text{ Mpc}^{-1}$.  Figure \ref{fig:plot_data} shows an example 
of the output for a particular cosmology. When we focus on $k$ values where $y_{\ell_r}$ 
is valid (center panel), the spatially correlated fluctuations of the low-resolution and 
high-resolution runs becomes apparent.
